Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-12-14 paper/main.tex
Added double sha256 vs single sha256 discussion

%FIXME: Nevn noe en plass om at vi kanskje burde timet kallene til HASH
%funksjonen også.

>>>>

%FIXME: Nevn noe en plass om at vi kanskje burde timet kallene til HASH
%funksjonen også.
\subsection{Impact of double \ac{SHA}-256}
The impact of using double \ac{SHA}-256 compared to single is suprisingly
small, even if you use the best-case estimate from Table
\ref{tbl:supercop:sha256}. For 1B, 1KB and 1MB files the data hashed is almost
exclusively 106B or less. If we assume data is hashed at the performance of 576
bytes, single \ac{SHA}-256 should outperform double \ac{SHA}-256 by about 10\%.
For 1B files this difference is eaten up by external factors (other
processes), the same goes for 1KB files. For 1MB files, there seems to be a
difference, however this difference is so small that we deem it unimportant.
For the larger files the performance penalty is even smaller, so all in all we
deem the performance penalty for Tahoe-\ac{LAFS} for using double \ac{SHA}-256
as opposed to single unimportant.
